Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-11-05 paper/paperv3.qmd
Adding a plot for the SMM talk on selective disappearance

>>>>

selective_diss_coef <- selective_coef %>% filter(model == "Base" | model == "Disappearance")

ggplot(selective_diss_coef, aes(hypothesis, mean, color = model)) + 
  geom_pointrange(aes(ymin = lwr, ymax = upr), position = position_dodge(width = 0.2)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = 0) + 
  labs(y = "Age Coefficient for Old Animals", x = "Model") + 
  scale_color_manual(values = c("#de77ae", "#00b6b9")) +
  scale_fill_manual(values = c("#de77ae", "#00b6b9")) +
  theme(legend.title = element_blank())
